Finance and Inequality - panel BMA approach\tnoteref{mytitlenote}

### 2020-02-13 Paper/elsarticle.tex
update

@@

\usepackage[utf8]{inputenc}

@@

\begin{abstract}
We investigate the impact of financial development on income inequality differentiating between depth, efficiency and access to financial markets and institutions. We apply panel Bayesian model averaging framework to address model uncertainty to reveal that financial development has complex relationship with the income distribution within countries. The access to and efficiency of banking decrease income inequality. The size of the markets has no relevance for overall income inequality, but relates to the higher top income shares. Moreover, unemployment along with investment into non-tangible assets increase income inequality while more redistribution imply lower levels of inequality.
\end{abstract}

>>>>

%!TEX program = pdflatex
%!BIB program = biber

@@

@@

\begin{abstract}
We investigate the impact of financial development on income inequality differentiating between depth, efficiency and access to financial markets and institutions. We apply panel Bayesian model averaging framework to address model uncertainty to reveal that financial development has complex relationship   with the income distribution within countries. The access to and efficiency of banking decrease income inequality. The size of the markets has no relevance for overall income inequality, but relates to the higher top income shares. Moreover, unemployment along with investment into non-tangible assets increase income inequality while more redistribution implies lower levels of inequality.
\end{abstract}
